---
title: "Asessment1.1"
author: "NhanVanCao4629397"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown editing

4. *The link between data, code and results make .Rmd powerful. You can share your entire workflow with your colleagues and they can quickly see your process*. **You can also write reports using .Rmd files which contain code and data analysis results. To enrich the document, you can add text, just like you would in a word document that describes your workflow, discusses your results and presents your conclusions - along side your analysis results**.

5. [link](https://rmarkdown.rstudio.com/lesson-8.html )

6.

```{r}
library(tidyverse)
fastfood<- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')


```

          
7. 
```{r}
library(tidyverse)
data(fastfood)
fastfood%>%head('fastfood',10)
```

```{r}
knitr::kable(fastfood[1:10,1:5])
```

8.Display the observations that has more than 1000 calories

```{r}
fastfood%>%filter(
  calories>=1000
  )
```

9.Save observations with more than 40 in total_fat and more than 80 in total_carb in a new variable (dataset) called `dont_eat_this`


```{r}
'dont_eat_this'<-
  fastfood%>%filter(
  total_fat>=40&total_carb>=80
  )
```

10.Using the initial dataset variable, display observations from restaurant Mcdonalds

- Save your .rmd file 

- Do a commit in Git tab

- Push in the same tab

```{r}
fastfood%>%filter(
  restaurant== "Mcdonalds"
)
```
