---
title: "Assessment1.2"
author: "NhanVanCao"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

11. Display the types of variables in the dataset using `skimr` package 
```{r}
install.packages(skimr)
library(skimr)
skim(fastfood)
```
12. Show the count of observations for each restaurant.
```{r}

fastfood%>%count(
  restaurant
)
```

)

13. Using grouppings (group_by()), summarise and display the average number of calories for each restaurant.

```{r}
fastfood%>%
group_by(restaurant)%>%summarise(average_calories_each_restaurant=mean(calories))
```

14. Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories`

```{r}
'average_calories'<-fastfood%>%
group_by(restaurant)%>%summarise(average_calories_each_restaurant=mean(calories))
```

15. Display the data visualization of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data visualization presents such information best. 
```{r}

fastfood%>% group_by(restaurant)%>%
        summarise(total_fat)
```
Two or more variables creates a bit more complexity. The best visualizations depend on whether the comparison is numeric to numeric, numeric to categorical, or categorical to categorical.

16. Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat` 


```{r}

'max_total_fat'<-fastfood%>%
group_by(restaurant)%>%
  mutate(max_total_fat = max(total_fat))%>%ungroup()

```
17. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 

- Save your .rmd file 

- Do a commit in Git tab

- Push in the same tab

```{r}
fastfood %>% 
  select(restaurant, sugar, protein)%>% filter(restaurant=="Mcdonalds")%>% 
  ggplot(aes(sugar,protein))+geom_point(colour = "red") +
  labs(x="Protein",y="Sugar",title="Mcdonalds",caption="Observation")
```

